Generality in food webs scales with species richness, not latitude

### 2015-03-20 manuscript/latitudepaper.tex
Brief note on scaling of TL's with lat.
Starting to rough out results.

@@

For relationships of $Z$, $G$, and $V$ to $S$, equation~\ref{LogLog} had a lower AIC than the corresponding
equation~\ref{Power}. This indicates that the data support an assumption of multiplicative log-normal
error better than an assumption of additive normal error. That is, [[but what does it mean?]] . 
We therefore used logarithmic-form models when assessing the effect of latitude on scaling relationships 
with $S$.

@@

@@

>>>>

[[Breaking things down by TL:

  Using proportions in main text following Riede et. al.

  With the subset of webs that actually have >0 BIT, there is a relationship between S, Gen, Vul, B, and T and Lat. Looks like this might be driven by outliers though... so gotta test that but might get to ignore things again.

]]

@@

For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{LogLog} had a
lower AIC than the corresponding equation~\ref{Power}. This indicates that the
data support an assumption of multiplicative log-normal error better than an
assumption of additive normal error. That is, models where $\epsilon$ is
modelled as an exponent to a multiplicative term (that is, an additive term on
the logarithmic scale) provide a better description of the data than models
where $\epsiolon$ is modelled as an additive term on the arithmetic scale
[[That's what this means... not sure if explaining it actually adds anything
though]] .  We therefore used logarithmic-form models when assessing the
effect of latitude on scaling relationships  with $S$.

@@

Considering only the subset of webs with at least one basal resource,
intermediate consumer, and top predator present, $S$, $Z$, and $V$ decreased with
latitude in stream webs but did not vary with latitude in other ecosystem types.
However, the relationships with latitude in stream webs [[Are they actually due to outliers?]]
The proportion of top predators in a food web decreased with increasing latitude in lake and
stream webs, while the proportion of basal resources increased with latitude in stream webs
[[Are these robust to outliers?]]

@@

\subsection*{Effect of Latitude on Scaling with B, I, and T}

As with scaling relationships with $S$, the effect of latitude on scaling relationships
with the proportions of basal resources, intermediate consumers, and top predators
varied across ecosystem types. Scaling of $Z$ with $B$ was stronger towards the equator in terrestrial
ecosystems, stronger towards the pole in lake, stream, and estuarine ecosystems, and did not vary
with latitude in Mairne ecosystems. Scaling of $Z$ with $I$ was not affected by latitude in any
ecosystem type, and scaling of $Z$ with $T$ was stronger towards the equator in stream and terrestrial
ecosystems but weaker towards the equator in all other ecosystem types. The differences in scaling
relationships over latitude were most dramatic in stream ecosystems.

Similar to the patterns observed for $Z$, scaling of $G$ with $B$ was stronger towards the poles
in stream, lake, and estuarine webs while marine and terrestrial webs showed very weak changes
in scaling relationships over latitude. Scaling of $G$ with $I$ was stronger towards the poles in stream
webs, but there was little effect of changing latitude on the scaling of $G$ with $I$ in other ecosystem
types. Scaling of $G$ with $T$ did not vary with latitude.
